\documentclass{lexnote}

\title{Sample: Intellectual Property Law}
\author{Jane Doe}
\date{\today}

\begin{document}
\maketitle
\tableofcontents

\section{Patent Law}

A \keyword{patent} grants an inventor the exclusive right to make, use, and sell an invention for a limited period.（专利权：发明人在一定期限内享有的排他性权利）

\begin{statute}[35 U.S.C. \S 101 -- Patentable Subject Matter]
  Whoever invents or discovers any new and useful process, machine,
  manufacture, or composition of matter, or any new and useful
  improvement thereof, may obtain a patent therefor.
\end{statute}

\begin{case}[Alice Corp. v. CLS Bank (2014)]
  The Supreme Court held that abstract ideas implemented on a generic
  computer are not patentable. A two-step test was established:
  (1) determine whether the claim is directed to an abstract idea;
  (2) search for an ``inventive concept'' that transforms the claim.
  （Alice 两步测试法：抽象概念 + 通用计算机实现 = 不可专利）
\end{case}

\begin{rul}[Novelty Requirement]
  An invention must be novel --- it cannot have been previously known,
  used, or described in any prior publication.（新颖性要求）
\end{rul}

\begin{notebox}[Review]
  The three core requirements for patentability: novelty, non-obviousness,
  and utility. Each must be independently satisfied.
\end{notebox}

\subsection{Claim Construction}

\begin{defbox}[Claim]
  The portion of a patent that defines the scope of legal protection.
  Claims are construed in light of the specification and prosecution history.
  （权利要求：界定专利保护范围的部分）
\end{defbox}

\todo{Add discussion on Markman hearings}

\section{Copyright Law}

\keyword{Copyright} protects original works of authorship fixed in a tangible medium of expression.（著作权：保护固定于有形介质的原创作品）

\begin{statute}[17 U.S.C. \S 107 -- Fair Use]
  Fair use factors: (1) purpose and character of use;
  (2) nature of the copyrighted work; (3) amount used;
  (4) effect on the market.
\end{statute}

\begin{case}[Google v. Oracle (2021)]
  The Supreme Court held that Google's copying of the Java SE API
  constituted fair use. The Court emphasized the transformative purpose
  and the importance of interoperability.（API 的复制可构成合理使用）
\end{case}

\end{document}
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
